---
title: "Tidy Tuesday Meetup"
subtitle: "2023: Pet Cats UK"
author: "Alice Walsh for R-Ladies Philly"
date: "2023-02-15"
output: 
  html_document:
    theme: lumen
    toc: true
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load_packages, echo=FALSE}
# This code chunk won't be displayed in final product because set echo=FALSE
library(dplyr)
library(ggplot2)
```

# Overview

Let's look at some fun data! 

https://github.com/rfordatascience/tidytuesday/blob/master/data/2023/2023-01-31/readme.md


# Load the data

```{r}
cats_uk <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2023/2023-01-31/cats_uk.csv')
cats_uk_reference <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2023/2023-01-31/cats_uk_reference.csv')

glimpse(cats_uk)
glimpse(cats_uk_reference)
```

# Ideas

+ Additional datasets for the US, Australia, and New Zealand are also available for download!
+ There is an article on this data - can we recreate or extend their findings?
+ Are older cats hunting less?
+ Make some sort of geo visualization or animation?
+ What makes a "super hunter"?

^ We worked with citizen scientists to track 925 pet cats from six countries, finding remarkably small home ranges (3.6 ± 5.6 ha). Only three cats ranged > 1 km2 and we found no relationship between home range size and the presence of larger native predators (i.e. coyotes, Canis latrans). Most (75%) cats used primarily (90%) disturbed habitats. Owners reported that their pets killed an average of 3.5 prey items/month, leading to an estimated ecological impact per cat of 14.2-38.9 prey ha−1 yr−1.


```{r}
cats_uk %>% 
  count(tag_id, sort = TRUE)
```

# Contact information
For any questions, contact <philly@rladies.org>
  