---
title: "Tidy Tuesday Meetup"
subtitle: "2023 week ?: Diwali Sales Data"
author: "Alice Walsh for R-Ladies Philly"
date: "2023-11-14"
output: 
  html_document:
    theme: lumen
    toc: true
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load_packages, echo=FALSE, warning=FALSE, message=FALSE}
# This code chunk won't be displayed in final product because set echo=FALSE
library(dplyr) # for data manipulation
library(ggplot2) # for plots
library(usemodels) # creates template code
library(tidymodels) # meta-package
theme_set(theme_light())
```

# Overview

We looked at two recent tidy tuesday datasets. 

1. Diwali sales data - but we struggled because the data had some weirdsies
2. Taylor Swift songs!

# Diwali Sales data

Let's look at some fun data as part of a tidy tuesday event. This week, the 
data is "Diwali Sales Data."

https://github.com/rfordatascience/tidytuesday/tree/master/data/2023/2023-11-14

https://www.kaggle.com/datasets/saadharoon27/diwali-sales-dataset

# Load the data

```{r}
sales <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2023/2023-11-14/diwali_sales_data.csv', show_col_types = FALSE)

glimpse(sales)
```

# Ideas

+ Map?
+ Predict sales?

# QUALITY CONTROL!!!

```{r}
# Do some visual inspection of the data - something looks weird with the USer_ID
# sales |> add_count(User_ID) |> View()
# explore some plots
count(sales, User_ID) |> pull(n) |> hist()
# Age by Amount
lm(Amount ~ Age, data = sales) |> broom::tidy()
lm(Amount ~ Age, data = sales) |> broom::glance()

sales |> 
  ggplot(aes(Age, Amount)) + 
  geom_point(alpha = 0.4) + 
  geom_smooth(method = "lm")

# Marital status
sales |> 
  distinct(User_ID, .keep_all = TRUE) |> 
  ggplot(aes(x = Marital_Status, y = Age, color = factor(Marital_Status))) + 
  geom_boxplot()

lm(Amount ~ Age + Marital_Status, data = sales) |> broom::tidy()
lm(Amount ~ Age, data = sales) |> broom::glance()

sales |> 
  ggplot(aes(Age, Amount, color = factor(Marital_Status))) + 
  geom_point(alpha = 0.4) + 
  geom_smooth(method = "lm")

```

Hm. The data seems to have some issues that make us suspicious

+ The counts of rows by user id do not match the Orders column
+ Some expected trends between demographic features are unlikely (many 12 year olds that are married)
+ The demographic data is inconsistent within user ids
+ Other columns do seem consistent (for example the value of different product categories)

Overall, we suspect some columns were merged incorrectly or otherwise corrupted earlier.

## check data direct from Kaggle

```{r}
# load the data downloaded direct from Kaggle
sales_kaggle <- readr::read_csv("~/Downloads/Diwali Sales Data.csv", show_col_types = FALSE)

all.equal(sales, sales_kaggle)
```

# NEW DATASET - Taylor Songs

See also: https://github.com/tashapiro/intro-observable 

Other ideas: Get the lyrics and get text embeddings!

- Check out hugging face APIs: https://huggingface.co/models
- Check out this API to get the full lyrics to songs: https://github.com/sarbor/taylor_swift_api

```{r}
taylor_album_songs <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2023/2023-10-17/taylor_album_songs.csv', show_col_types = F)
taylor_all_songs <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2023/2023-10-17/taylor_all_songs.csv', show_col_types = F)
taylor_albums <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2023/2023-10-17/taylor_albums.csv', show_col_types = F)

```

# Explore data

```{r}
taylor_album_songs |> 
  ggplot(aes(y = valence, x = mode_name)) + 
  geom_boxplot(outlier.shape = NA) + 
  geom_jitter(height = 0, width = 0.2) + coord_flip()

# Trends by minor or major key
taylor_album_songs |> 
  tidyr::pivot_longer(danceability:tempo, names_to = "metric") |>
  ggplot(aes(y = value, x = mode_name)) + 
  geom_boxplot(outlier.shape = NA) + 
  geom_jitter(height = 0, width = 0.2) + coord_flip() + 
  facet_wrap(~metric, scales = "free")
  
# Trends by minor or key signature
taylor_album_songs |> 
  tidyr::pivot_longer(danceability:tempo, names_to = "metric") |>
  ggplot(aes(y = value, x = time_signature)) + 
  # geom_boxplot(outlier.shape = NA) + 
  geom_jitter(height = 0, width = 0.2) + 
  coord_flip() + 
  facet_wrap(~metric, scales = "free")
  
# Trends over time
taylor_album_songs |> 
  mutate(track_release_year = lubridate::year(track_release)) |>
  tidyr::pivot_longer(danceability:tempo, names_to = "metric") |>
  ggplot(aes(y = value, x = track_release_year,
             color = track_release_year,
             group = track_release_year)) + 
  geom_boxplot(outlier.shape = NA) + 
  geom_jitter(height = 0, width = 0.2) + 
  facet_wrap(~metric, scales = "free")
```

```{r fig.height=8, fig.width=12}
# Trends by album name
taylor_album_songs |> 
  tidyr::pivot_longer(danceability:tempo, names_to = "metric") |>
  ggplot(aes(y = value, x = album_name, color = album_name)) + 
  geom_boxplot(outlier.shape = NA) + 
  geom_jitter(height = 0, width = 0.2) + 
  coord_flip() + 
  facet_wrap(~metric, scales = "free")
  
```

## How similar are the songs?

```{r}
# First check if there are any missing values in any columns
colSums(is.na(taylor_album_songs))

# Next created a reduced dataset with the numeric values of interest and removing missing values
taylor_filtered <- taylor_album_songs |> 
  select(track_name, danceability:tempo) |> 
  na.omit() |> 
  as.data.frame()

# Run principal components analysis with center and scale to generate a dimensionality reduction
mypca <- prcomp(taylor_filtered[, -1], center = T, scale. = T)

# plot 
cbind(mypca$x, taylor_filtered) |> 
  ggplot(aes(PC1, PC2, label = track_name)) + 
  ggrepel::geom_label_repel() + 
  geom_point() + 
  labs(title = "How similar are Taylor Songs?")

# Now just calculate a regular euclidean distance based on these variables
rownames(taylor_filtered) <- taylor_filtered$track_name

song_distances <- dist(scale(taylor_filtered[, -1])) |> broom::tidy()

song_distances |> 
  slice_min(distance, n = 5) |> 
  gt::gt()

```


## We confirmed via YouTube that the songs were similar

Links:

+ That’s When (Taylor’s Version) (From The Vault): https://www.youtube.com/watch?v=aOa6D6ku3dM
+ Bye Bye Baby (Taylor’s Version) (From The Vault): https://www.youtube.com/watch?v=yuFuwXd-B9E

Success!! But note that without centering and scaling the data first (`?scale`), the songs with the smallest distance were nothing alike! 

# Contact information
For any questions, contact <philly@rladies.org>
