---
title: "Tidy Tuesday Meetup"
subtitle: "2023 week 6: Big Tech Stock Prices"
author: "Alice Walsh for R-Ladies Philly"
date: "2023-02-15"
output: 
  html_document:
    theme: lumen
    toc: true
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load_packages, echo=FALSE}
# This code chunk won't be displayed in final product because set echo=FALSE
library(dplyr)
library(ggplot2)
library(gghighlight)
```

# Overview

Let's look at some fun data! 

https://github.com/rfordatascience/tidytuesday/tree/master/data/2023/2023-02-07


# Load the data

```{r}
big_tech_stock_prices <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2023/2023-02-07/big_tech_stock_prices.csv')
big_tech_companies <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2023/2023-02-07/big_tech_companies.csv')

glimpse(big_tech_stock_prices)
glimpse(big_tech_companies)
```

# Ideas

+ Make some plots or tables to explore the trends in prices
+ When did prices peak?
+ If you bought this stock ten years ago, what would your return be?
+ If you bought 52 week low, what would your return be?
+ Which stocks have done the best?
+ Integrate other data on these companies?
+ Add/find data on other non-big tech public companies?

```{r}
# How many rows per stock
count(big_tech_stock_prices, stock_symbol)

# get the highs, lows, averages per stock
summary_big_tech <- big_tech_stock_prices %>% 
        filter(date > "2010-01-01") %>% 
        group_by(stock_symbol) %>% 
        summarise(low = min(low),
                  high = max(high),
                  average_open = mean(open),
                  .groups = "drop")
```


### Plot

```{r}
# test gghighlight
big_tech_stock_prices %>% 
        ggplot(aes(x = date, y = open)) + 
        geom_line(aes(group = stock_symbol)) + 
        gghighlight(max(open) > 600) +
        theme_minimal()

# test ploty
myplot <- big_tech_stock_prices %>% 
        ggplot(aes(x = date, y = open)) + 
        geom_line(aes(group = stock_symbol))
library(plotly)
ggplotly(myplot)
```


## Add other companies to compare to big tech
```{r}
library(quantmod)
# https://www.nasdaq.com/market-activity/stocks/screener
mega_healthcare <- 
        c("ABBV",
          "AZN",
          "JNJ",
          "LLY",
          "MRK",
          "NVO",
          "PFE",
          "UNH")
all_stocks <- lapply(setNames(mega_healthcare, mega_healthcare),
                     function(x)
                             getSymbols(x, auto.assign = FALSE) %>%
                             as.data.frame() %>%
                             rename("open"=1,"high"=2,"low"=3,"close"=4,"volume"=5,"adjusted"=6) %>%
                             tibble::rownames_to_column(var = "date"))
all_stocks_df <- bind_rows(all_stocks, .id = "symbol")

glimpse(all_stocks_df)

healthcare <- all_stocks_df
names(healthcare) <- c("stock_symbol", "date", "open", "high", "low", "close", "volume", "adj_close")
healthcare$sector <- "healthcare"
big_tech_stock_prices$sector <- "tech"

healthcare <- rbind(big_tech_stock_prices, healthcare)

```

```{r}
# gghighlight with facet - add labels too
last_price <- healthcare %>% 
        group_by(stock_symbol) %>% 
        slice_max(date, n = 1)
healthcare %>% 
        ggplot(aes(x = date, y = open)) + 
        geom_line(aes(group = stock_symbol, color = sector)) + 
        facet_wrap(~sector, ncol = 1) + 
        # gghighlight can add labels with ggrepel, but we forced it!
        ggrepel::geom_label_repel(aes(label = stock_symbol, y = open, x = date),
                                  data = last_price) +
        gghighlight(label_key = NULL) +
        scale_color_manual(values = c("dodgerblue3", "goldenrod")) + 
        labs(y = "Opening Price", x = "Date",
             caption = "#TidyTuesday @RLadiesPhilly") + 
        theme_minimal() 

```

From here, it would be cool to make better plots that make it clearer what the trends were or to zoom in 
on some examples so that it was more legible. But great start for only 30 minutes!

# Contact information
For any questions, contact <philly@rladies.org>
