---
title: "Tidy Tuesday Meetup"
subtitle: "2023 week 7: Hollywood age gaps"
author: "Alice Walsh for R-Ladies Philly"
date: "2023-02-15"
output: 
  html_document:
    theme: lumen
    toc: true
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load_packages, echo=FALSE}
# This code chunk won't be displayed in final product because set echo=FALSE
library(dplyr)
library(ggplot2)
```

# Overview

Let's look at some fun data! 

https://github.com/rfordatascience/tidytuesday/tree/master/data/2023/2023-02-14


# Load the data

```{r}
age_gaps <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2023/2023-02-14/age_gaps.csv')

glimpse(age_gaps)
```

# Ideas

+ Are the age gaps between leads getting smaller or larger?
+ Can we make some interesting plots to show the trends over time?
+ Can we make an interesting table?
+ Maybe we can find additional data on the directors to merge in?
+ Maybe we can find additional data on the movies (e.g., [bechdel test data](https://github.com/rfordatascience/tidytuesday/blob/master/data/2021/2021-03-09/readme.md)) to add in?

```{r}
movies <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-03-09/movies.csv')

```

# Contact information
For any questions, contact <philly@rladies.org>
  