---
title: "Tidy Tuesday Meetup"
subtitle: "2023: Pet Cats UK"
author: "Alice Walsh for R-Ladies Philly"
date: "2023-02-15"
output: 
  html_document:
    theme: lumen
    toc: true
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load_packages, echo=FALSE}
# This code chunk won't be displayed in final product because set echo=FALSE
library(dplyr)
library(ggplot2)
library(sf)
```

# Overview

Let's look at some fun data! 

https://github.com/rfordatascience/tidytuesday/blob/master/data/2023/2023-01-31/readme.md


# Load the data

```{r}
cats_uk <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2023/2023-01-31/cats_uk.csv')
cats_uk_reference <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2023/2023-01-31/cats_uk_reference.csv')

glimpse(cats_uk)
glimpse(cats_uk_reference)
```

# Ideas

+ Additional datasets for the US, Australia, and New Zealand are also available for download!
+ There is an article on this data - can we recreate or extend their findings?
+ Are older cats hunting less?
+ Make some sort of geo visualization or animation?
+ What makes a "super hunter"?

^ We worked with citizen scientists to track 925 pet cats from six countries, finding remarkably small home ranges (3.6 ± 5.6 ha). Only three cats ranged > 1 km2 and we found no relationship between home range size and the presence of larger native predators (i.e. coyotes, Canis latrans). Most (75%) cats used primarily (90%) disturbed habitats. Owners reported that their pets killed an average of 3.5 prey items/month, leading to an estimated ecological impact per cat of 14.2-38.9 prey ha−1 yr−1.


```{r}
cats_uk %>% 
        count(tag_id, sort = TRUE)
```


## Maps?

Here is code shared during the R-Ladies/phillyRUG event on Feb 15th, 2023

```{r}
# shapefile
cats_uk_sf <- cats_uk %>% 
        left_join(cats_uk_reference) %>% 
        st_as_sf(coords = c("location_long", "location_lat"), 
                 crs = 4326)

uk <- map_data(map = "world", region = "UK") %>%
        filter(subregion == "Great Britain")
# st_as_sf(coords = c("long", "lat")) %>%
# st_crop(., xmin = -5.758854, xmax = -4.208614, ymin = 50.10352, ymax = 50.88222, crs = 4326)


mapTheme <- function(base_size = 12) {
        theme(
                text = element_text(color = "black", family="Avenir"),
                plot.title = element_text(size = 18,colour = "black", hjust = 0.5),
                plot.subtitle=element_text(face="italic", hjust = 0.5),
                plot.caption=element_text(size = 7, hjust = 0.5),
                axis.ticks = element_blank(),
                panel.background = element_blank(), 
                axis.text = element_blank(),
                panel.grid.minor = element_blank(),
                panel.border = element_rect(colour = "white", fill=NA, size=2)
        )
}

ggplot(uk) +
        # geom_polygon(fill = "gray", colour = "gray80", aes(x = long, y = lat, group = group)) +
        coord_map(xlim = c(-6, -4), ylim = c(50, 52), clip = "off") +
        geom_sf(data = cats_uk_sf, shape = 21, size = 3, aes(fill = log(ground_speed))) +
        scale_fill_distiller(palette = "YlGnBu", name = "Cat Speed") 

```


Simple plot without the map?

```{r}
cats_uk %>% 
        ggplot(aes(y = location_lat, x = location_long, fill = log10(ground_speed))) +
        geom_point(shape = 21, size = 3) + 
        scale_fill_distiller(palette = "YlGnBu", name = "Cat Speed") + 
        theme_minimal()

# Could we get the centroids of each cat? Then plot their max radii and color those?
```

# Contact information
For any questions, contact <philly@rladies.org>
